MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-04-26 manuscript/manuscript.qmd
add siPHD2 lactate flux data

We observed a similar effect of hypoxia on glycolysis when using RNA interference to silence PHD2 expression and activate HIF-1α gene transcription (**Figure 8 - figure supplement 1**).

These data indicate that the metabolic effects that we observe are not a consequence of off-target effects of BAY treatment.

>>>>

We observed a similar effect of hypoxia on glycolysis when using RNA interference to silence PHD2 expression and activate HIF-1α gene transcription (**Figure 8 - figure supplement 1**). As with BAY treatment, siPHD2 stabilized HIF-1α in normoxia and increased glycolytic gene expression (**Figure 8 - figure supplement 1B-E**); however, hypoxia inhibited siPHD2-dependent increaes in glycolysis (**Figure 8 - figure supplement 1F**). These data indicate that the metabolic consequences of PHD2 inhibition in normoxia and hypoxia are not simply a consequence of off-target effects of BAY treatment.
